Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-10-22 Methods-and-Results.Rmd
code hide fix

\subsection{General contact hypothesis}
```{r join data sets for analysis}
# Join aggregated data
avS1 <- dtWorkerSupp$workerAvFreQual %>%
  select(
    -ExternalReference
  ) %>%
  mutate(
    PID = c(1:nrow(.)),
    study = "S1"
  ) %>%
  select(PID, everything())
avS2 <- dtStudentSupp$studentContactFreq %>%
  mutate(
    study = "S2"
  )
avS3 <- dtMedicalSupp$medicalContactFreq %>%
  mutate(
    study = "S3"
  )

avAll <- bind_rows(avS1, avS2, avS3) %>%
  mutate(
    ID = c(1:nrow(.)),
    studyNum1 = ifelse(study == "S1", 1, 0),
    studyNum3 = ifelse(study == "S3", 1, 0)
  )
avAll$study2 <- relevel(as.factor(avAll$study),"S2")
```
```{r OLS regression across the three studies}
lmAllAttFreqQualX <-
  lm(
    AvAttitude ~ SumContactNL_c * AvQuality_c + SumContactNL_c * study2 + AvQuality_c * study2,
    data = avAll
  )

>>>>

\subsection{General contact hypothesis}

```{r join data sets for analysis, include=FALSE}
# Join aggregated data
avS1 <- dtWorkerSupp$workerAvFreQual %>%
  select(
    -ExternalReference
  ) %>%
  mutate(
    PID = c(1:nrow(.)),
    study = "S1"
  ) %>%
  select(PID, everything())
avS2 <- dtStudentSupp$studentContactFreq %>%
  mutate(
    study = "S2"
  )
avS3 <- dtMedicalSupp$medicalContactFreq %>%
  mutate(
    study = "S3"
  )

avAll <- bind_rows(avS1, avS2, avS3) %>%
  mutate(
    ID = c(1:nrow(.)),
    studyNum1 = ifelse(study == "S1", 1, 0),
    studyNum3 = ifelse(study == "S3", 1, 0)
  )
avAll$study2 <- relevel(as.factor(avAll$study),"S2")
```
```{r OLS regression across the three studies, include=FALSE}
lmAllAttFreqQualX <-
  lm(
    AvAttitude ~ SumContactNL_c * AvQuality_c + SumContactNL_c * study2 + AvQuality_c * study2,
    data = avAll
  )
